Data_visualization

### 2018-06-18 Rmd/Data_visualization.Rmd
adding colours to ggplot

library(ggplot2)
#load data

@@

# OVULES SOLANACEAE
p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "Ovules")+
theme(plot.title = element_text(hjust = 0.5))

>>>>

library(ggplot2)
library(colorspace)
colours <- rainbow_hcl(4, start = 30, end = 300)

#load data

@@

# OVULES SOLANACEAE
p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
theme(plot.title = element_text(hjust = 0.5))
